Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-01-03 p2/p2.Rmd
failed test info for comparison between profiles and signatures

```{r, fig.cap="Type II errors for different levels of coarseness."}
errors2 %>% filter(wv==30)%>% ggplot(aes(x = coarse, y=beta, colour=factor(alpha))) +
  geom_point() + geom_line() +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2")
```

@@

total1<- errors_sig_c %>% ggplot(aes(x = coarse, y=total, colour=factor(alpha), shape="signatures")) + geom_point() + geom_line()  + geom_point(data= errors2 %>% filter(wv==30), aes(shape="profiles")) + geom_line(data=errors2 %>% filter(wv==30), aes(shape="profiles")) + theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2")

total2<- wo120 %>% filter(wv>10) %>% ggplot(aes(x = wv, y=total, colour=factor(alpha), shape="signatures")) + geom_point() + geom_line() +geom_point(data=errors2 %>% filter(wv>10) %>% filter(coarse==0.25), aes(shape="profiles")) + geom_line(data=errors2 %>% filter(wv>10)%>% filter(coarse==0.25), aes(shape="profiles")) + theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2")

multiplot(total1, total2)
```
## Discussion

>>>>

```{r, fig.cap="Type II errors for different levels of coarseness of profiles."}
e1<-errors2 %>% filter(wv==30)%>% ggplot(aes(x = coarse, y=beta, colour=factor(alpha))) +
  geom_point() + geom_line() +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2") + xlab("Profile Coarseness")+
  ylab("Type II error")

e2<- errors_sig_c %>% filter(wv==30)%>% ggplot(aes(x = coarse, y=beta, colour=factor(alpha))) +
  geom_point() + geom_line() +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2")+ xlab("Signature Coarseness") + ylab("Type II error")

multiplot(e1,e2, cols = 1)

@@

total1<- errors_sig_c %>% ggplot(aes(x = coarse, y=total, colour=factor(alpha), shape="signatures")) + geom_point() + geom_line()  + geom_point(data= errors2 %>% filter(wv==30), aes(shape="profiles")) + geom_line(data=errors2 %>% filter(wv==30), aes(shape="profiles")) + theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2") + ylab("Total error")

total2<- wo120 %>% filter(wv>10) %>% ggplot(aes(x = wv, y=total, colour=factor(alpha), shape="signatures")) + geom_point() + geom_line() +geom_point(data=errors2 %>% filter(wv>10) %>% filter(coarse==0.25), aes(shape="profiles")) + geom_line(data=errors2 %>% filter(wv>10)%>% filter(coarse==0.25), aes(shape="profiles")) + theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2") + ylab("Total error")

```{r prof_missings, fig.width=8, fig.height=5, fig.cap="Number of failed tests by the window optimization size, wo, and ground truth. Test results from different sources have a much higher chance to fail, raising the question, whether failed tests should be treated as rejections of the null hypothesis of same source."}
nsp <- allp %>% group_by(wv, wo, match, coarse) %>% summarize(
  n_ss = mean(same_shift_n),
  n_ds = mean(diff_shift_n),
  zero_ss = sum(same_shift_n==0),
  zero_ds = sum(diff_shift_n==0),
  miss = sum(is.na(p_value)),
  missperc = miss/85491*100
)

ns_sig_c <- all_sig_c %>% group_by(wv, wo, match, coarse) %>% summarize(
  n_ss = mean(same_shift_n),
  n_ds = mean(diff_shift_n),
  zero_ss = sum(same_shift_n==0),
  zero_ds = sum(diff_shift_n==0),
  miss = sum(is.na(p_value)),
  missperc = miss/85491*100
)

#ns1<- ns[which(ns$wv == c(30,50), arr.ind = T),]
miss_1<- nsp %>% filter(wv == 30) %>%
#ns %>% filter(wv == c(30, 50)) %>%
  ggplot(aes(x = coarse, y = missperc, shape= "profile", colour = factor(match))) + 
  #geom_smooth(method="auto", size=.5, se=FALSE) +
  geom_point(size = 2) + 
  theme_bw() +
  ylab("Percent of failed tests.") +
  xlab("Coarseness") +
  scale_colour_brewer("Match", palette="Set1") + geom_point(data=ns  %>% filter(wv %in% c(30,50)) , aes(shape="signature"), size = 2)# + scale_colour_brewer("Match", palette="Set2") #+geom_smooth(method="auto", size=.5, se=FALSE) 
  #scale_shape_discrete("Size of \nvalidation\nwindow, #wv")

miss_2<- nsp %>% filter(coarse == 0.25) %>%
#ns %>% filter(wv == c(30, 50)) %>%
  ggplot(aes(x = wv, y = missperc, shape= "profile", colour = factor(match))) + 
  #geom_smooth(method="auto", size=.5, se=FALSE) +
  geom_point(size = 2) + 
  theme_bw() +
  ylab("Percent of failed tests.") +
  xlab("wv") +
  scale_colour_brewer("Match", palette="Set1") + geom_point(data=ns %>% filter(wo == 120)  %>% filter(coarse == 1) , aes(shape="signature"), size = 2) #+ scale_colour_brewer("Match", palette="Set2")

multiplot(plotlist = list(total1, total2, miss_1, miss_2), cols = 2)#, matrix(c(1,2,3,3), nrow=2, byrow=TRUE))
```

## Discussion
